### 2010-01-28 trunk/deliverables/D2_2_Ontology/fast_d2_2_2_ontology.tex
version for review
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@483 d8b0c59b-6544-0410-94d9-83a5658a058e

\usepackage{lastpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[pdfborder={0 0 0}]{hyperref}		% turn on when latex is used (not miktec)
\usepackage{url} % LEO: urls \url{}
\usepackage{verbatim} % code and comment
\usepackage{longtable}
\usepackage{xspace}   % whitespace after a macro if no punctuation after the macro
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable}
\usepackage{array}
\usepackage{amssymb}
\usepackage{paralist}

@@

@@

\begin{table}[h]
\caption{Different semantics for \texttt{isPositive}}
\label{tab:is_positive}
\begin{center}
\begin{tabular}{|l|c|c|}
\hline
& pre-condition & post-condition \\ \hline
\emph{isPositive ``YES''} & condition must be fulfilled & condition instantiated\\ \hline
\emph{isPositive ``NO''} & $\neg$condition must be fulfilled & instantiated condition removed \\ \hline
\end{tabular}
\end{center}
\end{table}

\subsection{Instance Examples} % (fold)
\label{sub:instance_examples}

\subsubsection{Complete Screen with Opaque Code} % (fold)
\label{ssub:complete_screen}

\singlespacing
\lstset{
	caption={Complete Screen with Opaque Code}, 
	label=list:screen_01
}
% \setlength\parindent{0in}
% \begin{minipage}[t]{\textwidth}
\lstinputlisting{exampleCode/01_screenExample.ttl}
% \end{minipage}
% \setlength\parindent{0.21in}
\doublespacing

% subsubsection complete_screen (end)

\subsubsection{Complete Screen with Declarative Definition} % (fold)
\label{ssub:complete_screen_with_declarative_definition}

\singlespacing
\lstset{
	caption={Complete Screen with Declarative Definition}, 
	label=list:screen_01
}
% \setlength\parindent{0in}
% \begin{minipage}[t]{\textwidth}
\lstinputlisting{exampleCode/02_screenExample.ttl}
% \end{minipage}
% \setlength\parindent{0.21in}
\doublespacing
% subsubsection complete_screen_with_declarative_definition (end)

% subsection instance_examples (end)

@@

A solution for representing pre- and post-conditions of screens and screen flows --- a central aspect of FAST technology --- has been proposed, which will now have to be implemented and tested both within the FAST catalogue and the FAST GVS.

@@

Finally, to contribute to a lasting legacy of the FAST project, the gadget ontology will serve as input to standardisation efforts for the definition of semantic gadgets, which will go beyond the scope of the project itself.
% section conclusions (end)

@@

\begin{figure}[h]
  \begin{center}
    \includegraphics[width=.82\linewidth]{images/fgo_uml_diagram}
    \caption{FAST Gadget Ontology Class Hierarchy}
    \label{fig:ontology_uml}
  \end{center}
\end{figure}

>>>>

\usepackage{lastpage}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage[pdfborder={0 0 0}]{hyperref}		% turn on when latex is used (not miktec)
\usepackage{url} % LEO: urls \url{}
\usepackage{verbatim} % code and comment
\usepackage{longtable}
\usepackage{xspace}   % whitespace after a macro if no punctuation after the macro
\usepackage{multirow}
\usepackage{colortbl}
\usepackage{longtable}
\usepackage{array}
\usepackage{booktabs}
\usepackage{amssymb}
\usepackage{paralist}

@@

\subsection{FAST Users} % (fold)
\label{sub:fast_users}

In modelling resources in FAST, the kind of users that are relevant are the users of the FAST tools themselves (i.e., the GVS), as opposed to end users of the gadgets. The following List.~\ref{list:user} shows how an individual user is modelled, using terminology from the FOAF and SIOC vocabularies.

\singlespacing
\lstset{
	caption={Basic description of a user in FAST}, 
	label=list:user,
	language=turtle
}
\begin{figure}[ht]
	\lstinputlisting{exampleCode/user_example_01.ttl}
\end{figure}
\doublespacing

Once a user has been defined in this way, they can e.g. be used to specify the creators of individual screen and screenflow resources, as shown in List.~\ref{list:creator}. This kind of creation metadata is being added to other metadata as shown in Sect.~\ref{sub:basic_annotation}.

\singlespacing
\lstset{
	caption={Modelling the creator of a resource}, 
	label=list:creator,
	language=turtle
}
\begin{figure}[ht]
	\lstinputlisting{exampleCode/user_example_02.ttl}
\end{figure}
\doublespacing

% subsection fast_users (end)

@@

\begin{table}[ht]
	\caption{Different semantics for \texttt{isPositive}}
	\label{tab:is_positive}
	\begin{center}

		\begin{tabular}{lcc}
			\toprule
			& \textbf{pre-condition} & \textbf{post-condition} \\ 
			\midrule
			\emph{isPositive ``YES''} & condition must be fulfilled & condition instantiated\\ 
			\emph{isPositive ``NO''} & $\neg$condition must be fulfilled & instantiated condition removed \\ 
			\bottomrule
		\end{tabular}
	\end{center}
\end{table}

% 
% \subsection{Instance Examples} % (fold)
% \label{sub:instance_examples}
% 
% \subsubsection{Complete Screen with Opaque Code} % (fold)
% \label{ssub:complete_screen}
% 
% \singlespacing
% \lstset{
% 	caption={Complete Screen with Opaque Code}, 
% 	label=list:screen_01
% }
% % \setlength\parindent{0in}
% % \begin{minipage}[t]{\textwidth}
% \lstinputlisting{exampleCode/01_screenExample.ttl}
% % \end{minipage}
% % \setlength\parindent{0.21in}
% \doublespacing
% 
% % subsubsection complete_screen (end)
% 
% \subsubsection{Complete Screen with Declarative Definition} % (fold)
% \label{ssub:complete_screen_with_declarative_definition}
% 
% \singlespacing
% \lstset{
% 	caption={Complete Screen with Declarative Definition}, 
% 	label=list:screen_02
% }
% % \setlength\parindent{0in}
% % \begin{minipage}[t]{\textwidth}
% \lstinputlisting{exampleCode/02_screenExample.ttl}
% % \end{minipage}
% % \setlength\parindent{0.21in}
% \doublespacing
% % subsubsection complete_screen_with_declarative_definition (end)
% 
% % subsection instance_examples (end)

@@

A solution for representing pre- and post-conditions of screens and screen flows --- a central aspect of FAST technology --- has been presented, as it has been implemented and tested both within the FAST catalogue and the FAST GVS.

@@

% Finally, to contribute to a lasting legacy of the FAST project, the gadget ontology will serve as input to standardisation efforts for the definition of semantic gadgets, which will go beyond the scope of the project itself.
% section conclusions (end)

@@

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.82\linewidth]{images/fgo_uml_diagram}
    \caption{FAST Gadget Ontology Class Hierarchy}
    \label{fig:ontology_uml}
  \end{center}
\end{figure}
